A 38 Million Year Old Neptune-Sized Planet in the Kepler Field

### 2021-11-30 paper_review/response_1.txt

REVIEWER COMMENT
----------
One note about the transit analysis: The MuSCAT3 data was introduced as
supporting evidence but the conclusion (that the transits appear achromatic)
was never explicitly stated.

RESPONSE
----------
> Line 642 of the original manuscript notes "Although we did not
> detect the RM anomaly, the multi-band MuSCAT3 light curves show that
> the transit is achromatic (Figure 7)."

REVIEWER COMMENT
----------
Line 725: The fast rotation period and flares could plausibly effect the
completeness.

RESPONSE
----------
> These completeness statistics were computed using KeplerPORTS (the Burke &
> Catanzarite 2021 citation).  KeplerPORTS corrects for red noise in the light
> curves by using the CDPP over different timescales -- see Section 3.3 of
> Burke, C. J. & Catanzarite, J.  2017, Planet Detection Metrics: Per-Target
> Detection Contours for Data Release 25, KSCI-19111-002.  This correction is
> performed using both a) the slope of the RMS CDPP versus transit duration for
> for "long" transit durations (the average of 7.5, 9.0, 10.5, 12.0, 12.5, and
> 15.0 hours) and b) the same slope for "short" transit durations (2.0, 2.5,
> 3.0, 3.5, and 4.5 hours). We retrieved these values from the DR25 Kepler
> occurrence rate products hosted on the NASA Exoplanet Archive.  For Kepler
> 1627, they were CDPP_long = 0.25478 and CDPP_short=0.79505.  Per Figure 2 of
> the KSCI-19111-002 memo, these do indeed indicate a noisy star -- no
> surprises.
>
> We've added a sentence to the manuscript to clarify that we are talking about
> per-target detection contours, which should correct for the impact of at
> least the fast rotation period, inasmuch as it manifests in the slope of the
> CDPP versus transit duration.  We have also modified the wording for clarity,
> and have added a citation to Burke & Catanzarite's 2017 KSCI-19111-002 memo.
>
> To determine whether this CDPP-based detection efficiency correction is
> *accurate* given the exact red-noise properties of Kepler-1627 (i.e., the
> rotation and flares), a full injection-recovery analysis of the light curve
> with a pipeline of our own would be necessary. This effort is outside our
> scope, for now.

@@

REVIEWER COMMENT
----------
Lines 530-542: does option (ii) include a transit fit as well? I assume it does
but it would be good to clarify. And is option (i) the 2nd and 4th order
polynomial? Perhaps just state this?

RESPONSE
----------
> Yes, option (ii) includes the transit -- we've updated this in the text for
> clarity.
>
> Yes, option (i) is the 2nd or 4th order polynomial.  We've updated the text
> to state this more directly as well.  Thank you!

REVIEWER COMMENT
----------
Line 561-562: do the authors mean "lack of statistical significance"?

RESPONSE
----------
> Yes -- we've added this to the text.  Thank you.

@@

REVIEWER COMMENT
----------
Section 4.2

Analysis of the motion of the photocentroid has been widely used to help
validate Kepler planets. Can this be used here to distinguish between the
possible A and B host stars?

RESPONSE
----------
> Kepler-1627B is ~0.16 arcseconds East of Kepler-1627A.  For the sake of
> argument, assume it contributes 2% of the flux to the aperture (an
> overestimate), and neglect other stars in the scene. 
>
> Taking the origin at Kepler-1627A, the center of light outside of transit is
> then roughly (0.98*0 arcsec + 0.02*0.16 arcsec) = 0.0032 arcsec due East of
> the primary.
>
> During transit, if the transit happens on the primary, the center of light is
> roughly ( (0.98-0.002)*0 arcsec + (1-(0.98-0.002))*0.16 arcsec ) = 0.0035
> arcsec due East of the primary -- i.e., it is closer to the secondary by 0.3
> milliarcseconds, since the primary is getting fainter.
>
> If the transit instead happened on the secondary, the center of light would
> be roughly (0.98*0 arcsec + (0.9*0.02)*0.16 arcsec) ~= 0.00288 arcsec due
> East of the primary, where a 10% intrinsic eclipse depth on the secondary is
> required to fit the observed transit depth.  In this scenario, the centroid
> would shift closer to the *primary* by 0.3 milliarcseconds.
>
> Examining the NASA SPOC Data Validation Report (DVR), there are two available
> photocentroid tests, the first based on the flux-weighted centroid analysis,
> and the second based on the difference image centroid offset test.  The
> latter test yields offset uncertainties of ~100 milliarcsec for Kepler-1627,
> which is far above the relevant signal.  The former test yields centroid peak
> RA and DEC offsets consistent with zero, with uncertainties of 0.9 and 1.1
> milliarcsec respectively (page 19 of 552 in the DR25 DVR).  So, given that
> the quoted centroid precision uncertainties are a factor of ~3 larger than
> the expected shift, it is not possible to use the test in a way that
> distinguishes the two host stars in a statistically convincing way.

@@

REVIEWER COMMENT
----------
Line 604-608: The statement that the density from the transit duration is
inconsistent with that expected for the M dwarf "B" cites Table 2 and
Choi+2016, but that Table does not appear to provide any information on "B",
and the Choi+2016 reference is just for the Mesa models. A density of 2 g/cm3
(or lower) is possible for an M dwarf on the pre-main sequence, depending on
the mass, age and model used.

RESPONSE
----------
> Thank you for catching this -- this citation is indeed deprecated and
> erroneously was not updated during the writing process.  The final adopted
> calculation was based on the masses and radii from the Baraffe+2015 models,
> rather than the MESA models (Choi+2016).  The Baraffe models are available
> from
> http://perso.ens-lyon.fr/isabelle.baraffe/BHAC15dir/BHAC15_tracks+structure.
>
> We believe that the companion's mass is roughly between 0.3 and 0.4 Msun, and
> that the age of the system is ~38 +/- 6 Myr.  The Baraffe models give:
>
>    32 Myr 0.300 Msun, 0.481 Rsun, 3.80 g / cm3
>    35 Myr 0.300 Msun, 0.465 Rsun, 4.21 g / cm3
>    40 Myr 0.300 Msun, 0.443 Rsun, 4.86 g / cm3
>    32 Myr 0.400 Msun, 0.555 Rsun, 3.30 g / cm3
>    35 Myr 0.400 Msun, 0.537 Rsun, 3.64 g / cm3
>    40 Myr 0.400 Msun, 0.514 Rsun, 4.15 g / cm3
>    32 Myr 0.330 Msun, 0.506 Rsun, 3.60 g / cm3
>    35 Myr 0.330 Msun, 0.489 Rsun, 3.98 g / cm3
>    40 Myr 0.330 Msun, 0.467 Rsun, 4.58 g / cm3
>
> i.e., our default assumption was 40 Myr and 0.33 Msun.  The age is adopted
> for the reasons discussed in the text.  The mass is based off
> the observed deltaMag in 832nm and K' (3.14 +/- 0.15 and 2.37 +/- 0.02
> respectively), which implies absolute magnitudes for the secondary of K'=XXX and
> [832]=YYY.  Based on a set of absolute magnitude and color relations from a
> submitted paper by A. Kraus, these gave ~=0.33 Msun.  (TODO: NEED TO BEEF
> THIS UP!)
>
> The plausible range of companion densities is therefore 3.30 g/cc to
> 4.86 g/cc.  We've updated the text to reflect this uncertainty, but
> it doesn't change the overall point that our measured stellar
> density (2.00+/-0.24 g/cc) is still a fair bit lower than the
> expected range.

TODO TODO REMOVE THIS
> As a sanity check, these calibrations find that for a companion spectral type
> of M2.5, one expects colors of G-K'=3.39 mag and G-[832] = 1.51 mag, though
> we cannot test this since Gaia DR2/EDR3 does not resolve the secondary.
>
> For the primary spectral type of G8, one expects G-K'=1.58 mag and G-[832] =
> 0.71 mag (i.e., K'=13.02-1.58=11.44, and [832]=G-0.71=12.31 for the primary).
> So it holds together (bolstering the case for it being a bound companion) to
> find DeltaK' = 2.37 mag and Delta[832] = 3.14 mag.

G8V: M_G = 5.098
M2.5V: M_G = 9.67 (ZAMS).
-> delta G = 9.67 - 5.098 = 4.57, so G =13.02+4.57= 17.592 for secondary
-> G-K'=3.39mag implies K' = 14.20 for secondary
-> G-[832]=1.51mag implies [832] = 16.08 for secondary
->
-> expected delta K' = 2.76
-> expected delta 832 = 3.78
.. (both are observed a bit lower!  i.e., it's not red enough)

@@

REVIEWER COMMENT
----------
Lines 613-614: it would be good to quantify this, i.e. how faint an unresolved
companion or background star must be based on the star's position in the CMD.

RESPONSE
----------
> Visually, one can see that the width of the single-star sequence of δ Lyr
> candidates (black points) in the upper-right panel of Figure 3 is <~0.2 mag.
> So, if we saw a star with the same (BP-RP) color as Kepler 1627 that were
> >~0.3 mag brighter in M_G, we would classify it as a likely photometric
> binary.  This means we are able to exclude stars ~0.32* as bright as the
> primary (in Gaia G-band). This corresponds to excluding bound companions more
> massive than ~0.85 Msun (the primary's mass is ~0.95 Msun).  The SB2 tests do
> much better if the velocity separation exceeds the CCF width (down to 1% as
> bright as the primary;
> https://ui.adsabs.harvard.edu/abs/2015AJ....149...18K/abstract).  For
> brevity, we would prefer to not present this information in the text.

@@

REVIEWER COMMENT
----------
Lines 635-638: Here, new observations appear for the first time but are not
described. While the details are given in the appendix, and the outcome of the
observations doesn't define this work, the authors need to give some basic
description of the observations, e.g. passbands, SNR, resolution, observation
times, etc. The authors should not assume the reader actually know what HIRES
and MuSCAT are!

RESPONSE
----------
> Thank you for this suggestion.  The main text now reads
>
> "We observed a transit of Kepler-1627 Ab on the night of 2021 Aug 7
> spectroscopically with HIRES at the Keck-I telescope and photometrically in
> $griz$ bands with MuSCAT3 at Haleakal\=a Observatory.  Details of the
> observation sequence are discussed in Appendix C; Figure 7 shows the
> results."
>
> The first paragraph of Appendix C has been significantly modified to include
> the requested additional information, including the passbands, exposure
> times, S/N, and instrument resolution.  Regarding observation times, "the
> night of 2021 Aug 7" is sufficiently precise for the purposes of the text;
> Tables 5 and 6 have the BJD-TDB timestamps for those who desire greater
> precision.

@@

REVIEWER COMMENT
----------
Section 5

line 670: assuming that SNR is not to blame, the problem is not precision, the
problem is either measuremnt systematics or astrophysical noise.

RESPONSE
----------
> Thank you for this point; we've updated the text to say "signal-to-noise"
> rather than "precision".

@@

REVIEWER COMMENT
----------
line 678-683: The Ca II HK activity indicator "S" as well as the H-alpha
equivalent width could be obtained from the HIRES spectrum. Have the authors
checked fora X-ray or UV (Galex) detection of this star? The star is likely not
detected but its worth a look. In the same vein, the authors may wish to
comment on whether the star's infrared emission indicates or rule out a
substantial debris disk -- the star is detected in WISE (and perhaps Spitzer?)

RESPONSE
----------
> Regarding the S-values, they are shown in the second panel of Figure 7, and
> are also reported in Table 6.  The line profile changes shown in Figure 12
> suggested that the majority of the RV variation observed was due to
> starspot-induced variations.  Quantitative measurements of the H-alpha EWs
> are not expected to change this picture, and so we opt to not include them.
>
> Regarding the NIR, UV, and X-ray detections, we searched Vizier within a
> radius of 4 arcseconds.
>
> For the NIR and the possibility of a debris disk, Kepler-1627 is detected in
> W1, W2, W3, and W4 (see kepler1627_vizier_photometry.png attached).  While W4
> might be in excess of the usual Rayleigh-Jeans tail (and this could be
> quantified by fitting synthetic stellar atmospheres), quantifying this excess
> is best done at the population level, especially given the calibration
> uncertainties that are present in W4 (e.g., Cotten & Song 2016, ApJS 225 15).
> Since Kepler-1627 has not been identified as even a candidate debris disk
> host in the previous literature, we opt to not speculate on this topic.
>
> For the UV, Olmedo+2015 reported a coincident source with NUVmag of 19.052
> +/- 0.017 [AB mags], with a NUV S/N of 65 (2015, ApJ, 813, 100). Loyd et al
> 2020 report a NUV flux of 4e-13 +/- 4e-15 mW/m^2.  We can use this detection
> as a youth indicator (e.g., Figure 9 of Newton+2021, which Newton et al
> attribute from the idea in Shkolnik+2011, ApJ 727 6. Since for Kepler 1627
> 2MASS J = 11.690+/-0.021 (Cutri+2003), we have m_NUV-m_J = 7.36.  Given the
> (BP-RP)0 of ~0.95... FIXME TODO ARE YOU GOING TO MAKE A WHOLE NEW PLOT FOR
> THIS DAMN THING?  MIGHT BE WORTHWHILE... QUICK VETTING CHECK FOR ANY G AND K
> TYPE STARS IN THE CLUSTER...
>
> For the X-ray (i.e., ROSAT), there were no reported detections in Vizier.

@@

REVIEWER COMMENT
----------
lines 699-701 It could be mentioned here that the planet orbital period and
stellar rotational period are not a rational combination.

RESPONSE
----------
> Done, thank you.

REVIEWER COMMENT
----------
line 723-726: The caveat that should be mentioned here is that this is for
older, main sequence stars.

RESPONSE
----------
> The first reviewer had a similar comment -- our response is the same:
>
> These completeness statistics were computed using KeplerPORTS (the Burke &
> Catanzarite 2021 citation).  KeplerPORTS corrects for red noise in the light
> curves by using the CDPP over different timescales -- see Section 3.3 of
> Burke, C. J. & Catanzarite, J.  2017, Planet Detection Metrics: Per-Target
> Detection Contours for Data Release 25, KSCI-19111-002.  This correction is
> performed using both a) the slope of the RMS CDPP versus transit duration for
> for "long" transit durations (the average of 7.5, 9.0, 10.5, 12.0, 12.5, and
> 15.0 hours) and b) the same slope for "short" transit durations (2.0, 2.5,
> 3.0, 3.5, and 4.5 hours). We retrieved these values from the DR25 Kepler
> occurrence rate products hosted on the NASA Exoplanet Archive.  For Kepler
> 1627, they were CDPP_long = 0.25478 and CDPP_short=0.79505.  Per Figure 2 of
> the KSCI-19111-002 memo, these do indeed indicate a noisy star -- no
> surprises.
>
> We've added a sentence to the manuscript to clarify that we are talking about
> per-target detection contours, which should correct for the impact of at
> least the fast rotation period, inasmuch as it manifests in the slope of the
> CDPP versus transit duration.  We have also modified the wording for clarity,
> and have added a citation to Burke & Catanzarite's 2017 KSCI-19111-002 memo.
>
> To determine whether this CDPP-slope detection efficiency correction is
> *accurate* given the exact red-noise properties of Kepler-1627 (i.e., the
> rotation and flares), a full injection-recovery analysis of the light curve
> with a pipeline of our own would be necessary. This effort is outside our
> scope, for now.

### 2021-11-30 paper/ms.tex
[WIP] reviewer #2 staging

We then cleaned the candidate TESS rotation period measurements
through a combination of automated and manual steps.  \deleted{As a
matter of scope, we restricted our attention to the \nkinwithtess\
stars discussed in Section~\ref{sec:kinematicselection} in the spatial
and kinematic proximity of Kepler\,1627.}  \deleted{Kepler rotation
periods were derived by \citet{mcquillan_rotation_2014} for 28 of
\replaced{these }{our \nkinwithtess\ }stars; for these cases, we
simply adopted the Kepler rotation period.} \added{First, to validate
the TESS rotation periods, we compared against 28 stars
from \citet{mcquillan_rotation_2014} that were also observed by Kepler.  Of the 23 stars with Kepler
periods below 10 days, 21 of the TESS periods agreed with the Kepler
rotation periods; the other 2 were measured at the double-period
harmonic.  Of the remaining 5 stars with Kepler rotation periods above
10 days, none were correctly recovered by TESS (3 were near the
half-period harmonic).  We therefore adopted a general stance of
caution for TESS rotation periods exceeding 10 days, and used the
Kepler rotation periods for the stars for which they were available.}
For the remaining stars with only TESS data, we
focused only on the stars for which no companions were known with a brightness
exceeding one-tenth of the target star in a $21\farcs0$ radius.  There
were \nkinwithtessandcrowding\ stars that met these crowding requirements, and
that had TESS data available.  For plotting purposes we then imposed a
selection based on the strength of the signal itself: we required the
Lomb Scargle power to exceed 0.2, and the period to be below 15\,days.

@@

\begin{figure}[tp]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.45\textwidth]{f7.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Keck/HIRES radial velocities and MuSCAT3 photometry from the transit of 2021 Aug 7.}
		{\it Top:} 
		The radial velocity jitter across the 15~minute exposures
		($\sigma_{\rm RV}\approx30$\ms) prevented us from detecting the RM
		effect;
		a model including the RM anomaly and a quadratic trend in time to
		fit the spot-induced $\approx$\,$250$\ms\ trend is shown (see
		Appendix~\ref{app:rm}).  Shaded bands show 2-$\sigma$ model
		uncertainties.  
		{\it Middle:} The RV variations are strongly correlated with varying
		emission in the Ca H and K lines.
		{\it Bottom}: The photometric transit depths are consistent across
		the {\it griz} bandpasses. The photometry is binned at 10~minute
		intervals.
		\label{fig:ground}
	}
\end{figure}
\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{f8.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Radii, orbital periods, and ages of transiting exoplanets}.
		Planets younger than a gigayear with ${\rm \tau}/\sigma_{\tau} >
		3$ are emphasized, where $\tau$ is the age and $\sigma_{\tau}$ is
		its uncertainty.  \pn\ is shown with a star.  The large sizes of
		the youngest transiting planets could be explained by their
		primordial atmospheres not yet having evaporated; direct
		measurements of the atmospheric outflows or planetary masses would
		help to confirm this expectation.  Selection effects may also be
		important.  Parameters are from the NASA Exoplanet Archive (2021
		Sept 15).
		\label{fig:rp_period_age}
	}
\end{figure*}

@@

Beyond this simple test, a line of evidence that
effectively confirms the planetary interpretation is that the stellar density
implied by the transit duration and orbital period is inconsistent
with an eclipsing body around the M-dwarf companion.  We find
$\rho_\star = 2.00 \pm 0.24\,{\rm g\,cm}^{-3}$, while the
theoretically expected density for Kepler\,1627B is $\approx 4.6\,{\rm
g\,cm}^{-3}$ (Table~\ref{tab:posterior}; \citealt{choi_mesa_2016}).
The transit duration is therefore too long to be explained by a star
eclipsing the M dwarf secondary at $10$-$\sigma$.  While the planet
might hypothetically still orbit a hidden close and bright companion,
this possibility is implausible given {\it i)} the lack of secondary
lines in the HIRES spectra, {\it ii)} the lack of secondary
rotation signals in the Kepler photometry, and {\it iii)} the proximity
of \sn\ to the \cn\ locus on the Gaia CAMD (Figure~\ref{fig:age}).

@@

A third supporting line of evidence for the planetary interpretation
also exists.  We observed a transit of \pn\ on the
night of 2021 Aug 7 simultaneously with Keck/HIRES and MuSCAT3.  We
scheduled the observations using the ephemeris of
\citet{holczer_transit_2016}.  Although we did not detect the
Rossiter-McLaughlin (RM) anomaly, the multi-band MuSCAT3 light curves
show that the transit is achromatic (Figure~\ref{fig:ground}).
Quantitatively, when we fitted the MuSCAT3
photometry with a model that lets the transit depths vary across each
bandpass, we found {\it griz} depths consistent with the Kepler depth
at 0.6, 0.3, 0.3, and 1.1-$\sigma$ respectively.  Conditioned on the
ephemeris and transit depth from the Kepler data, the MuSCAT3 observations also
suggested a transit duration $17.3\pm4.3\ {\rm min}$ shorter than the
Kepler transits.
However, given both the lack of TDVs in the Kepler data
and the relatively low signal-to-noise of the MuSCAT3 transit,
further photometric follow-up would be necessary to determine
whether the transit duration is indeed changing.  
For our RM analysis,
the details are discussed in Appendix~\ref{app:rm}.  While the
velocities are marginally more consistent with a prograde or polar
orbit than a retrograde orbit, the spot-corrected exposure-to-exposure
scatter ($\sigma_{\rm RV}\approx 30$\ms) is comparable to the expected
RM anomaly assuming an aligned orbit ($\Delta v_{\rm RM}\approx
20\,{\rm m\,s}^{-1}$).  We are therefore not in a position to claim a
spectroscopic detection of the RM effect, nor to quantify the stellar
obliquity.

@@

Kepler\,1627Ab provides a new extremum in the ages of the Kepler
planets, and opens multiple avenues for further study.  Observations
of spectroscopic transits at greater precision should yield a
measurement of the stellar obliquity, which would confirm or refute
the prograde orbital geometry suggested by the TTV-local slope
correlation.  Separately, transit spectroscopy aimed at detecting
atmospheric outflows could yield insight into the evolutionary state
of the atmosphere \citep[{\it
e.g.},][]{ehrenreich_giant_2015,spake_helium_2018,vissapragada_2020}.
Observations that quantify the amount of high-energy
irradiation incident on the planet would complement these efforts, by
helping to clarify the expected outflow rate \citep[{\it
e.g.},][]{poppenhaeger_2021}.  Finally, a challenging but informative
quantity to measure would be the planet's mass. Measured at
sufficient precision,
for instance through a multi-wavelength radial velocity campaign,
the combination of the size, mass, and age 
would yield constraints on both the planet's composition and its
initial entropy \citep{owen_constraining_2020}.

More immediately, the Kepler data may yet contain additional
information.  For instance, one possible explanation for the transit
asymmetry shown in Figure~\ref{fig:lc} is that of a dusty asymmetric
outflow.  
Dusty outflows are theoretically
expected for young mini-Neptunes, and the amplitude of the observed
asymmetry is consistent with predictions \citep{wang_dai_2019}.
A second possibility is that the planetary orbit is slightly
misaligned from the stellar spin axis, and tends to transit starspot
groups at favored stellar latitudes.  
This geometry would be necessary in order to
explain how the starspot crossings could add up coherently.
Other possibilities including
gravity darkening or TTVs causing the asymmetry are disfavored (see
Appendix~\ref{app:asymmetry}).

@@

In the context of the transiting planet population, \pn\ is among the
youngest known (Figure~\ref{fig:rp_period_age}).  Comparable systems
with precise ages include K2-33
\citep{Mann_K2_33b_2016,David_et_al_2017}, DS~Tuc
\citep{benatti_possibly_2019,newton_tess_2019} , HIP~67522
\citep{rizzuto_tess_2020}, TOI~837 \citep{bouma_cluster_2020}, the
two-planet AU~Mic \citep{plavchan_planet_2020,martioli_aumicbc_2021}
and the four-planet V1298~Tau \citep{david_four_2019}.  \pn\ is one of
the smaller planets in this sample ($3.82\pm0.16\,R_\oplus$), which
could be linked to the selection effects imposed by spot-induced
photometric variability at very young ages \citep[{\it
e.g.},][]{zhou_2021_tois}.  However, smaller planets could have been
detected: the Kepler pipeline's median completeness extended to
$1.6\,R_\oplus$ at 10~day orbital periods, and $3.3\,R_\oplus$ at
100~days \citep{2021ascl.soft07027B}.  The large size of \pn\ relative
to most Kepler mini-Neptunes might therefore support a picture
in which the typical $5\,M_\oplus$ to 10$\,M_\oplus$ mini-Neptune
\citep{wu_mass_2019} loses a significant fraction of its primordial
atmosphere over its first gigayear
\citep{Owen_Wu_2013,ginzburg_corepowered_2018}.  
\added{This of course depends on the mass of \pn; an alternative
explanation for its large size could simply be that it is more massive
than the typical Kepler mini-Neptune, or that it has an abnormally
large envelope to core mass ratio.}

@@

\section{Spectroscopy and Photometry During the Transit of 2021 Aug 7}
\label{app:rm}

>>>>

We then cleaned the candidate TESS rotation period measurements
through a combination of automated and manual steps.  \deleted{As a
matter of scope, we restricted our attention to the \nkinwithtess\
stars discussed in Section~\ref{sec:kinematicselection} in the spatial
and kinematic proximity of Kepler\,1627.}  \deleted{Kepler rotation
periods were derived by \citet{mcquillan_rotation_2014} for 28 of
our \nkinwithtess\ stars; for these cases, we
simply adopted the Kepler rotation period.} \added{First, to validate
the TESS rotation periods, we compared against 28 stars
from \citet{mcquillan_rotation_2014} that were also observed by Kepler.  Of the 23 stars with Kepler
periods below 10 days, 21 of the TESS periods agreed with the Kepler
rotation periods; the other 2 were measured at the double-period
harmonic.  Of the remaining 5 stars with Kepler rotation periods above
10 days, none were correctly recovered by TESS (3 were near the
half-period harmonic).  We therefore adopted a general stance of
caution for TESS rotation periods exceeding 10 days, and used the
Kepler rotation periods for the stars for which they were available.}
For the remaining stars with only TESS data, we
focused only on the stars for which no companions were known with a brightness
exceeding one-tenth of the target star in a $21\farcs0$ radius.  There
were \nkinwithtessandcrowding\ stars that met these crowding requirements, and
that had TESS data available.  For plotting purposes we then imposed a
selection based on the strength of the signal itself: we required the
Lomb Scargle power to exceed 0.2, and the period to be below 15\,days.

@@

\begin{figure}[tp]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.45\textwidth]{f7.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Keck/HIRES radial velocities and MuSCAT3 photometry from the transit of 2021 Aug 7.}
		{\it Top:} 
		The radial velocity jitter across the 15~minute exposures
		($\sigma_{\rm RV}\approx30$\ms) prevented us from detecting the RM
		effect;
		a model including the RM anomaly and a quadratic trend in time to
		fit the spot-induced $\approx$\,$250$\ms\ trend is shown (see
		Appendix~\ref{app:groundobs}).  Shaded bands show 2-$\sigma$ model
		uncertainties.  
		{\it Middle:} The RV variations are strongly correlated with varying
		emission in the Ca H and K lines.
		{\it Bottom}: The photometric transit depths are consistent across
		the {\it griz} bandpasses. The photometry is binned at 10~minute
		intervals.
		\label{fig:ground}
	}
\end{figure}
\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{f8.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Radii, orbital periods, and ages of transiting exoplanets}.
		Planets younger than a gigayear with ${\rm \tau}/\sigma_{\tau} >
		3$ are emphasized, where $\tau$ is the age and $\sigma_{\tau}$ is
		its uncertainty.  \pn\ is shown with a star.  The large sizes of
		the youngest transiting planets could be explained by their
		primordial atmospheres not yet having evaporated; direct
		measurements of the atmospheric outflows or planetary masses would
		help to confirm this expectation.  Selection effects may also be
		important.  Parameters are from the NASA Exoplanet Archive (2021
		Sept 15).
		\label{fig:rp_period_age}
	}
\end{figure*}

@@

Beyond this simple test, a line of evidence that
effectively confirms the planetary interpretation is that the stellar density
implied by the transit duration and orbital period is inconsistent
with an eclipsing body around the M-dwarf companion.  We find
$\rho_\star = 2.00 \pm 0.24\,{\rm g\,cm}^{-3}$, while the
theoretically expected density for Kepler\,1627B is $\approx 4.6\,{\rm
g\,cm}^{-3}$ \citep{baraffe_new_2015}.
The transit duration is therefore too long to be explained by a star
eclipsing the M dwarf secondary at $10$-$\sigma$.  While the planet
might hypothetically still orbit a hidden close and bright companion,
this possibility is implausible given {\it i)} the lack of secondary
lines in the HIRES spectra, {\it ii)} the lack of secondary
rotation signals in the Kepler photometry, and {\it iii)} the proximity
of \sn\ to the \cn\ locus on the Gaia CAMD (Figure~\ref{fig:age}).

@@

A third supporting line of evidence for the planetary interpretation
also exists.  We observed a transit of \pn\ on the
night of 2021 Aug 7 \replaced{simultaneously with Keck/HIRES and
MuSCAT3}{spectroscopically with HIRES at the Keck-I telescope and photometrically in
$griz$ bands with MuSCAT3 at Haleakal\=a Observatory}.  \added{
Details of the observation sequence are discussed in
Appendix~\ref{app:groundobs}; Figure~\ref{fig:ground} shows the
results.}\deleted{.  We
scheduled the observations using the ephemeris of
\citet{holczer_transit_2016}.}  Although we did not detect the
Rossiter-McLaughlin (RM) anomaly, the multi-band MuSCAT3 light curves
show that the transit is achromatic\deleted{
  (Figure~\ref{fig:ground})}.
Quantitatively, when we fitted the MuSCAT3
photometry with a model that lets the transit depths vary across each
bandpass, we found {\it griz} depths consistent with the Kepler depth
at 0.6, 0.3, 0.3, and 1.1-$\sigma$ respectively.  \added{The
achromatic transits strongly favor Kepler\ 1627A as the transit host,
since Kepler\ 1627B is much redder.}  Conditioned on the
ephemeris and transit depth from the Kepler data, the MuSCAT3 observations also
suggested a transit duration $17.3\pm4.3\ {\rm min}$ shorter than the
Kepler transits.
However, given both the lack of TDVs in the Kepler data
and the relatively low signal-to-noise of the MuSCAT3 transit,
further photometric follow-up would be necessary to determine
whether the transit duration is indeed changing.  
For our RM analysis,
the details are discussed in Appendix~\ref{app:groundobs}.  While the
velocities are marginally more consistent with a prograde or polar
orbit than a retrograde orbit, the spot-corrected exposure-to-exposure
scatter ($\sigma_{\rm RV}\approx 30$\ms) is comparable to the expected
RM anomaly assuming an aligned orbit ($\Delta v_{\rm RM}\approx
20\,{\rm m\,s}^{-1}$).  We are therefore not in a position to claim a
spectroscopic detection of the RM effect, nor to quantify the stellar
obliquity.

@@

Kepler\,1627Ab provides a new extremum in the ages of the Kepler
planets, and opens multiple avenues for further study.  Observations
of spectroscopic transits at greater
\replaced{precision}{signal-to-noise} should yield a
measurement of the stellar obliquity, which would confirm or refute
the prograde orbital geometry suggested by the TTV-local slope
correlation.  Separately, transit spectroscopy aimed at detecting
atmospheric outflows could yield insight into the evolutionary state
of the atmosphere \citep[{\it
e.g.},][]{ehrenreich_giant_2015,spake_helium_2018,vissapragada_2020}.
Observations that quantify the amount of high-energy
irradiation incident on the planet would complement these efforts, by
helping to clarify the expected outflow rate \citep[{\it
e.g.},][]{poppenhaeger_2021}.  Finally, a challenging but informative
quantity to measure would be the planet's mass.  Measured at
sufficient precision,
for instance through a multi-wavelength radial velocity campaign,
the combination of the size, mass, and age 
would yield constraints on both the planet's composition and its
initial entropy \citep{owen_constraining_2020}.

More immediately, the Kepler data may yet contain additional
information.  For instance, one possible explanation for the transit
asymmetry shown in Figure~\ref{fig:lc} is that of a dusty asymmetric
outflow.  
Dusty outflows are theoretically
expected for young mini-Neptunes, and the amplitude of the observed
asymmetry is consistent with predictions \citep{wang_dai_2019}.
A second possibility is that the planetary orbit is slightly
misaligned from the stellar spin axis, and tends to transit starspot
groups at favored stellar latitudes.  
This geometry would be necessary in order to
explain how the starspot crossings could add up coherently\added{,
given that the planetary orbital period (7.203\,days) and the stellar
rotation period (2.642\,days) are not a rational combination}.
Other possibilities including
gravity darkening or TTVs causing the asymmetry are disfavored (see
Appendix~\ref{app:asymmetry}).

@@

In the context of the transiting planet population, \pn\ is among the
youngest known (Figure~\ref{fig:rp_period_age}).  Comparable systems
with precise ages include K2-33
\citep{Mann_K2_33b_2016,David_et_al_2017}, DS~Tuc
\citep{benatti_possibly_2019,newton_tess_2019}, HIP~67522
\citep{rizzuto_tess_2020}, TOI~837 \citep{bouma_cluster_2020}, the
two-planet AU~Mic \citep{plavchan_planet_2020,martioli_aumicbc_2021}
and the four-planet V1298~Tau \citep{david_four_2019}.  \pn\ is one of
the smaller planets in this sample ($3.82\pm0.16\,R_\oplus$), which
could be linked to the selection effects imposed by spot-induced
photometric variability at very young ages \citep[{\it
e.g.},][]{zhou_2021_tois}.  \replaced{However,}{However, it seems that} smaller planets could have been
detected: \added{based on the per-target detection contours, }the Kepler pipeline's median completeness extended to
$1.6\,R_\oplus$ at 10~day orbital periods, and $3.3\,R_\oplus$ at
100~days
\citep{2021ascl.soft07027B}.
\added{These limits account for the spot-induced variability in the
system through
a correction based on the Combined Differential Photometric Precision
(CDPP) in the \sn\ light curve over the relevant transit timescales
\citep{2017ksci.rept...19B}.} The large size of \pn\ relative
to most Kepler mini-Neptunes might therefore support a picture
in which the typical $5\,M_\oplus$ \deleted{to 10$\,M_\oplus$} mini-Neptune
\citep{wu_mass_2019} loses a significant fraction of its primordial
atmosphere over its first gigayear
\citep{Owen_Wu_2013,ginzburg_corepowered_2018}.  
\added{This of course would need to be confirmed through a measurement
of the planetary mass; alternative explanations for its large size
could be that it is abnormally massive, or that it has an abnormally
large envelope to core mass ratio.}

@@

\section{Spectroscopy and Photometry During the Transit of 2021 Aug 7}
\label{app:groundobs}
